*Prochlorococcus marinus* responses to light and oxygen

### 2024-06-04 Output/PLOSRound2/ResponsetoReviewers.txt

Figures 3 through 8: These figures are obviously the crux of the results in this paper, but as they are 
currently presented it is relatively difficult to think clearly about them. I feel like they could be combined 
into 2 or 3 full page figures which might make it easier to make the relevant comparisons; either by 
combining the two types of figure (growth rates and model fits) for each ecotype, or else all the growth 
rate curves together in one figure and all the model plots together in another.

- Thank you for this suggestion. We combined the growth rate figure with the GAM model for each strain to faciliate comparisons.

I'm also not sure I understand why the red light data is relevant -- perhaps by moving it to supplemental, it would be easier to compile these data into compound figures?

We briefly motivated the inclusion of the red light growth trials, as mechanistically informative, at line XXX:
" As mentioned, growth rate trials under red light, although not representative of *P. marinus* niches, are mechanistically informative [@murphyPhotoinactivationPhotosystemII2017] regarding photoinactivation of PSII."

-Through the Discussion, notably under the discussion of the GAM models and responses to growth rate to increasing PUR, we return to the responses to red light to show that some 'high light' limitations on growth are interpretable as photoinhibition of PSII, which is more severe under blue, compared to red, light, notably at lines XXXX-1032 (xXXX).

@@

Figure S4 ? It is very hard to see the fit lines other than the pooled fit. Consider using different colors 
and solid lines since this is online.

-We edited the figure to clarify the fit lines:
Line: XXX

Table 1: The trees described in the legend should be included in the supplemental material.

-Thank you for bringing this to our attention. We clarified the wording on line XXXX of the revised manuscripted. "Protein homologies for FtsH isoforms between *Prochlorococcus marinus* and *Synechocystis* were extracted from @bonisteelStrainSpecificDifferences2018."

### 2024-06-05 Code/Manuscript_O2.Rmd
Zorz added

Proteins from *P. marinus* were detected across depths and oxygen concentrations in the OPP data set [@saitoPeptidesTheirSpectral2018]. We focused our analyses on core photosynthetic protein complexes, annotated as coming from clades HLI (2 strains, including strain MED4 ); LLI (2 strains, including strain NATL2A); LLII/III (2 strains, including strain SS120) and LLIV (2 strains, including MIT9313) (Fig \@ref(fig:CladeProchloroPhotosynthDepthO2)), as a function of depth (a
proxy for light level) and measured [O~2~] at the sampling locations. Photosynthetic complexes
from clades HLI and LLI were detected throughout the water column, although predominately at stations with high [O~2~]. Though present in the genome of MED4, the absence of proteins annotated as RUBISCO complex for clade HLI, compared to annotated
detections of RUBISCO across the other three clades, suggests
limitations in the annotation process assigning highly conserved protein
sequences to clades. Notwithstanding limitations on assignments of proteins to clades, detections of the abundant carbon fixation complex RUBISCO derived from clades HLI, LLI and LLII/III were notably absent from stations at low [O~2~], suggesting limited capacity for carbon fixation by clades HLI,  LLI and LLII/LLIII under low [O~2~] habitats. Clade LLII/LLIII
photosynthetic complexes were detected throughout the sampled ranges of depth/light and [O~2~], with  detections of proteins at both high and low [O~2~], compared to other strains. Complexes from LLIV (including strain MIT9313) were detected across the depth/light and [O~2~] ranges, with more detections at deeper, darker depths and at low [O~2~], compared to other clades.  We note that detections of photosynthetic proteins from strain MIT9313 (dark symbols) show a particular bias towards low [O~2~] sampling stations, compared to the wider detections of clade LLIV. Our analyses utilized a proteomics dataset; however, alternate approaches, such as metagenomics or metatranscriptomics, could have been employed to analyze ecotype abundances using the TARA Oceans [@pesantOpenScienceResources2015] or other datasets.

>>>>

Proteins from *P. marinus* were detected across depths and oxygen concentrations in the OPP data set [@saitoPeptidesTheirSpectral2018]. We focused our analyses on core photosynthetic protein complexes, annotated as coming from clades HLI (2 strains, including strain MED4 ); LLI (2 strains, including strain NATL2A); LLII/III (2 strains, including strain SS120) and LLIV (2 strains, including MIT9313) (Fig \@ref(fig:CladeProchloroPhotosynthDepthO2)), as a function of depth (a
proxy for light level) and measured [O~2~] at the sampling locations. Photosynthetic complexes
from clades HLI and LLI were detected throughout the water column, although predominately at stations with high [O~2~]. Though present and expressed in the genome of MED4 [@zorzRUBISCOPhotosystemII2015], the absence of proteins annotated as RUBISCO complex for clade HLI, compared to annotated detections of RUBISCO across the other three clades, suggests
limitations in the annotation process assigning highly conserved protein
sequences to clades. Notwithstanding limitations on assignments of proteins to clades, detections of the abundant carbon fixation complex RUBISCO derived from clades HLI, LLI and LLII/III were notably absent from stations at low [O~2~], suggesting limited capacity for carbon fixation by clades HLI,  LLI and LLII/LLIII under low [O~2~] habitats. Clade LLII/LLIII
photosynthetic complexes were detected throughout the sampled ranges of depth/light and [O~2~], with  detections of proteins at both high and low [O~2~], compared to other strains. Complexes from LLIV (including strain MIT9313) were detected across the depth/light and [O~2~] ranges, with more detections at deeper, darker depths and at low [O~2~], compared to other clades.  We note that detections of photosynthetic proteins from strain MIT9313 (dark symbols) show a particular bias towards low [O~2~] sampling stations, compared to the wider detections of clade LLIV. Our analyses utilized a proteomics dataset; however, alternate approaches, such as metagenomics or metatranscriptomics, could have been employed to analyze ecotype abundances using the TARA Oceans [@pesantOpenScienceResources2015] or other datasets.
